\begin{thebibliography}{10}

\bibitem{perna2019}
Perna, D., \& Tagarelli, A. (2019). 
\textit{Deep auscultation: Predicting respiratory anomalies and diseases via recurrent neural networks}. 
Proceedings of the 2019 IEEE International Conference on Bioinformatics and Biomedicine (BIBM), 2821–2827.

\bibitem{demir2021}
Demir, F., \& Sengur, A. (2021).
\textit{A deep CNN-LSTM model for classification of lung sounds}.
Biomedical Signal Processing and Control, 70, 102896.

\bibitem{ibrahim2020}
Ibrahim, A., \& Hussain, A. (2020).
\textit{Lung sound classification using recurrent neural networks and short-time Fourier transform}.
Computers in Biology and Medicine, 122, 103771.

\bibitem{aygun2022}
Aygun, M., \& Sert, E. (2022).
\textit{Respiratory sound classification using EfficientNet and spectrogram augmentation}.
IEEE Access, 10, 45329–45340.

\bibitem{icbhi2017}
Rocha, B. M., Filos, D., Mendes, L., Vogiatzis, I., Perantoni, E., Kaimakamis, E., ... \& Nascimento, J. C. (2017).
\textit{An open access database for the evaluation of respiratory sound classification algorithms}.
Physiological Measurement, 38(9), N1–N13.

\bibitem{hsu2023clap}
Hsu, W.-H., Lee, H.-Y., Yang, P.-H., Nagrani, A., Shor, J., Ferrer, L., \& Lopez Moreno, I. (2023). 
\textit{CLAP: Learning Audio-Text Joint Embeddings from Large-Scale Webly-Supervised Data}. 
arXiv preprint arXiv:2302.03102.

\bibitem{lewis2020rag}
Lewis, P., Perez, E., Piktus, A., Petroni, F., Karpukhin, V., Goyal, N., ... \& Riedel, S. (2020). 
\textit{Retrieval-Augmented Generation for Knowledge-Intensive NLP Tasks}. 
arXiv preprint arXiv:2005.11401.

\bibitem{vaswani2017attention}
Vaswani, A., Shazeer, N., Parmar, N., Uszkoreit, J., Jones, L., Gomez, A. N., Kaiser, Ł., \& Polosukhin, I. (2017).  
\textit{Attention Is All You Need}.  
Advances in Neural Information Processing Systems, 30 (NeurIPS 2017).

\bibitem{jurafsky2023slp3}
Jurafsky, D., \& Martin, J. H. (2023). 
\textit{Speech and Language Processing} (3rd ed. draft). 
Retrieved from \url{https://web.stanford.edu/~jurafsky/slp3/}

\bibitem{flutterdocs}
Google. (2023). 
\textit{Flutter Documentation}. 
Retrieved from \url{https://docs.flutter.dev/}

\bibitem{huggingface}
Hugging Face. (2023). 
\textit{Transformers Documentation}. 
Retrieved from \url{https://huggingface.co/docs/transformers/index}

\bibitem{bge2024}
Xu, Canwen, Xiao, Yixin, Ma, Yutai, Ji, Heng, \& Wang, Yining. (2024).  
\textit{BGE-M3: A Versatile Embedding Model for Retrieval, Classification, and Re-ranking}.  
arXiv preprint arXiv:2403.03692.


\end{thebibliography}
